---
title: "Hipps9.20.2019"
author: "JReceveur"
output: 
  html_document:
    code_folding: hide
toc: true
toc_depth: 3
toc_float: true
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=14, fig.height=10)
knitr::opts_chunk$set(fig.align="center")
```
```{r}
#From https://gist.github.com/grabear/018e86413b19b62a6bb8e72a9adba349
#Parse Silva function
parse_taxonomy_silva_128 <- function(char.vec){
  # Use default to assign names to elements in case problem with greengenes prefix
  char.vec = parse_taxonomy_default(char.vec)
  # Check for unassigned taxa
  if (char.vec["Rank1"] == "Unassigned") {
    char.vec <- c(Rank1="D_0__Unassigned", Rank2="D_1__Unassigned", Rank3="D_2__Unassigned", Rank4="D_3__Unassigned",
                  Rank5="D_4__Unassigned", Rank6="D_5__Unassigned", Rank7="D_6__Unassigned")
  }
  # Define the meaning of each prefix according to SILVA taxonomy
  Tranks = c(D_0="Kingdom", D_1="Phylum", D_2="Class", D_3="Order", D_4="Family", D_5="Genus", D_6="Species")
  # Check for prefix using regexp, warn if there were none. trim indices, ti
  ti = grep("[[:alpha:]]\\_[[:digit:]]{1}\\_\\_", char.vec)
  if( length(ti) == 0L ){
    warning(
      "No silva prefixes were found. \n",
      "Consider using parse_taxonomy_delfault() instead if true for all OTUs. \n",
      "Dummy ranks may be included among taxonomic ranks now."
    )
    # Will want to return without further modifying char.vec
    taxvec = char.vec
    # Replace names of taxvec according to prefix, if any present...
  } else {
    # Format character vectors for Ambiguous taxa
    if( length(ti) < 7 ){
      for (key in names(char.vec)) {
        if ( char.vec[key] == "Ambiguous_taxa" ) {
          tax_no <- (as.numeric(substr(key, 5, 5)) - 1)
          char.vec[key] = sprintf("D_%s__Ambiguous_taxa", tax_no)
        }
      }
      # Reset the trimmed indicies if Ambiguous taxa
      ti = grep("[[:alpha:]]\\_[[:digit:]]{1}\\_\\_", char.vec)
    }
    # Remove prefix using sub-"" regexp, call result taxvec
    taxvec = gsub("[[:alpha:]]\\_[[:digit:]]{1}\\_\\_", "", char.vec)
    # Define the ranks that will be replaced
    repranks = Tranks[substr(char.vec[ti], 1, 3)]
    # Replace, being sure to avoid prefixes notK present in Tranks
    names(taxvec)[ti[!is.na(repranks)]] = repranks[!is.na(repranks)]
  }
  return(taxvec)
}

```

```{r ,warning=FALSE,include=FALSE}
library(vegan)
library(MASS)
library(ggplot2)
library(plyr)
library(dplyr)
library(magrittr)
library(scales)
library(grid)
library(reshape2)
library(phyloseq)
library(randomForest)
library(knitr)
library(ape)
library(ggpubr)
library(agricolae)
library(Rmisc)
library(multcompView)
set.seed(1256)
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#000000","#CC79A7")
theme_set(theme_bw(base_size = 18)+theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
biom=import_biom("HippoWTax9.18.19.biom",parseFunction= parse_taxonomy_silva_128)
#tax_table(biom) <- tax_table(biom)[,-c(5:10,14)]#remove dummy ranks

metadata=read.table("HippoMetadataWDiversity9.18.19.tsv",header = TRUE)
#metadata$BSpecies = factor(metadata$BSpecies, levels = c("SubmergedFresh","EarlyFloating","Floatingdecay","Advancedfloatingdecay","SunkenRemains")) #fixes x-axis labels

tree=read_tree("tree9.18.19.nwk")

sampdat=sample_data(metadata)
sample_names(sampdat)=metadata$id
physeq=merge_phyloseq(biom,sampdat,tree)
#physeq=rarefy_even_depth(physeq, 5000, replace = TRUE, trimOTUs = TRUE, verbose = TRUE,rngseed = TRUE) Rarefied to ____ in QIIME
```



##Data overview{.tabset}
###Sequencing
```{r}
physeq

Trtdata <- ddply(metadata, c("BSpecies","Month"), summarise,
                 N    = length(id),
)
Trtdata

head(metadata)
```

###Metadata
```{r}
metadata

```



##Alpha Diversity {.tabset}
###Observed Species BSpecies

```{r}
plot_richness(physeq, x="BSpecies",color="BSpecies", measures=c("Observed"))+geom_boxplot(aes(x=BSpecies, y=value, color=BSpecies), alpha=0.05)+ylab("Observed Species")+geom_point(size=3)+guides(fill=FALSE)

```

###Shannon Diversity BSpecies
```{r}
#By Year
kruskal.test( shannon~ BSpecies, data=metadata)

#By species
av=kruskal.test( shannon~ BSpecies, data=metadata) #fig.width = 8, fig.height = 8 for line above to change size
posthoc<-compare_means(shannon ~ BSpecies, data = metadata, p.adjust.method = "fdr")


Hyphenated<-as.character(paste0(posthoc$group1,"-",posthoc$group2))
difference<-posthoc$p.format
names(difference)<-Hyphenated

Letters<-multcompLetters(difference)

#posthoc <- HSD.test(av,"BSpecies",group=TRUE)

stats<-summarySE(metadata,measurevar="shannon",groupvars=c("BSpecies",na.rm=TRUE))
ggplot(stats,aes(x=BSpecies,y=shannon,fill=BSpecies))+geom_bar(stat="identity")+
  geom_errorbar(aes(ymin=shannon-se,ymax=shannon+se),color="black")+
  geom_text(aes(x=BSpecies, y=shannon+se+0.5,label=Letters$Letters), position=position_dodge(width=0.9), size=8,color="black")+ #Write in labels from posthoc
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ scale_fill_manual(values=cbPalette)+xlab("")+ylab("Shannon Diversity")+labs(fill="Decomposition Stage")+guides(fill=FALSE)#+ theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95))

av
posthoc
Letters
stats

```

###Faith's PD BSpecies
```{r, FaithPD}
#By year
kruskal.test( faith_pd~ BSpecies, data=metadata)
#By species
av=kruskal.test( faith_pd~ BSpecies, data=metadata) #fig.width = 8, fig.height = 8 for line above to change size
posthoc<-compare_means(faith_pd ~ BSpecies, data = metadata, p.adjust.method = "fdr")



Hyphenated<-as.character(paste0(posthoc$group1,"-",posthoc$group2))
difference<-posthoc$p.format
names(difference)<-Hyphenated

Letters<-multcompLetters(difference)
stats<-summarySE(metadata,measurevar="faith_pd",groupvars=c("BSpecies",na.rm=TRUE))
ggplot(stats,aes(x=BSpecies,y=faith_pd,fill=BSpecies))+geom_bar(stat="identity")+
  geom_errorbar(aes(ymin=faith_pd-se,ymax=faith_pd+se),color="black")+
  geom_text(aes(x=BSpecies, y=faith_pd+se+0.5,label=Letters$Letters), position=position_dodge(width=0.9), size=8,color="black")+ guides(fill=FALSE)+  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ scale_fill_manual(values=cbPalette)+xlab("")+ylab("Faith's PD")+labs(fill="Decomposition Stage")#+ theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95))

av
posthoc
Letters
stats


```

###RTHA subset
```{r}
RTHA<-subset(metadata,BSpecies=="RTHA")
kruskal.test( faith_pd~ Month, data=RTHA)
kruskal.test( shannon~ Month, data=RTHA)

kruskal.test( faith_pd~ Year, data=RTHA)


kruskal.test( shannon~ Year, data=RTHA)



```
###Observed Species Month

```{r}
plot_richness(physeq, x="Month",color="Month", measures=c("Observed"))+geom_boxplot(aes(x=Month, y=value, color=Month), alpha=0.05)+ylab("Observed Month")+geom_point(size=3)+guides(fill=FALSE)

```

###Shannon Diversity Month
```{r}
av=kruskal.test( shannon~ Month, data=metadata) #fig.width = 8, fig.height = 8 for line above to change size
posthoc<-compare_means(shannon ~ Month, data = metadata, p.adjust.method = "fdr")


Hyphenated<-as.character(paste0(posthoc$group1,"-",posthoc$group2))
difference<-posthoc$p.format
names(difference)<-Hyphenated

Letters<-multcompLetters(difference)

#posthoc <- HSD.test(av,"Month",group=TRUE)

stats<-summarySE(metadata,measurevar="shannon",groupvars=c("Month",na.rm=TRUE))
ggplot(stats,aes(x=Month,y=shannon,fill=Month))+geom_bar(stat="identity")+
  geom_errorbar(aes(ymin=shannon-se,ymax=shannon+se),color="black")+
  geom_text(aes(x=Month, y=shannon+se+.5,label=Letters$Letters), position=position_dodge(width=0.9), size=8,color="black")+ #Write in labels from posthoc
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ scale_fill_manual(values=cbPalette)+xlab("")+ylab("Shannon Diversity")+labs(fill="Decomposition Stage")+guides(fill=FALSE)#+ theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95))

av
posthoc
Letters
stats

```

###Faith's PD Month
```{r, FaithPD2}
av=kruskal.test( faith_pd~ Month, data=metadata) #fig.width = 8, fig.height = 8 for line above to change size
posthoc<-compare_means(faith_pd ~ Month, data = metadata, p.adjust.method = "fdr")


Hyphenated<-as.character(paste0(posthoc$group1,"-",posthoc$group2))
difference<-posthoc$p.format
names(difference)<-Hyphenated

Letters<-multcompLetters(difference)
stats<-summarySE(metadata,measurevar="faith_pd",groupvars=c("Month",na.rm=TRUE))
ggplot(stats,aes(x=Month,y=faith_pd,fill=Month))+geom_bar(stat="identity")+
  geom_errorbar(aes(ymin=faith_pd-se,ymax=faith_pd+se),color="black")+
  geom_text(aes(x=Month, y=faith_pd+se+0.5,label=Letters$Letters), position=position_dodge(width=0.9), size=8,color="black")+ guides(fill=FALSE)+  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ scale_fill_manual(values=cbPalette)+xlab("")+ylab("Faith's PD")+labs(fill="Decomposition Stage")#+ theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95))

av
posthoc
Letters
stats


```



##Taxa Plots {.tabset}

```{r filteringForFamily2}


GPr  = transform_sample_counts(physeq, function(x) x / sum(x) ) #transform samples based on relative abundance
PhylumAll=tax_glom(GPr, "Phylum")

PhylumLevel = filter_taxa(PhylumAll, function(x) mean(x) > 1e-4, TRUE) #filter out any taxa lower tha 0.1%
FamilyAll=tax_glom(GPr,"Family")
FamilyLevel = filter_taxa(FamilyAll, function(x) mean(x) > 1e-3, TRUE) #filter out any taxa lower tha 1%
GenusAll=tax_glom(GPr,"Genus")
GenusLevel = filter_taxa(GenusAll, function(x) mean(x) > 1e-3, TRUE) #filter out any taxa lower tha 1%

plot_bar(PhylumLevel,x="id", y="Abundance",fill="Phylum")+ scale_fill_manual(values=cbPalette)+xlab("Sample ID")+ylab("Relative Abundance (>0.01%)")

plot_bar(FamilyLevel,x="id", y="Abundance",fill="Family")+ scale_fill_manual(values=cbPalette)+xlab("Sample ID")+ylab("Relative Abundance (>0.1%)")

plot_bar(GenusLevel,x="id", y="Abundance",fill="Genus")+ scale_fill_manual(values=cbPalette)+xlab("Sample ID")+ylab("Relative Abundance (>0.1%)")


```

###Phylum Level


The top 5 phyla across all samples are given in the table below
```{r PhylumRA, warning=FALSE}
df <- psmelt(PhylumLevel)
df$Abundance=df$Abundance*100
Trtdata <- ddply(df, c("Phylum", "BSpecies"), summarise,
                 N    = length(Abundance),
                 mean = mean(Abundance),
                 sd   = sd(Abundance),
                 se   = sd / sqrt(N)
)
df2 <- psmelt(PhylumAll)
df2$Abundance<-df2$Abundance*100
PhylumAll<-ddply(df2, c("Phylum"), summarise,
                 N    = length(Abundance),
                 mean = mean(Abundance),
                 sd   = sd(Abundance),
                 se   = sd / sqrt(N)
)
PhylumSorted<-PhylumAll[order(-PhylumAll$mean),]
PhylumSorted[1:5,]

PhylumAll2<-ddply(df2, c("Phylum","BSpecies"), summarise, #For Rel abu tabs
                  N    = length(Abundance),
                  mean = mean(Abundance),
                  sd   = sd(Abundance),
                  se   = sd / sqrt(N)
)
PhylumSorted2<-PhylumAll2[order(-PhylumAll$mean),]

PhylumAll3<-ddply(df, c("Phylum","Month","BSpecies"), summarise, #For Rel abu tabs
                  N    = length(Abundance),
                  mean = mean(Abundance),
                  sd   = sd(Abundance),
                  se   = sd / sqrt(N)
)

```



```{r TreatmentPlot5}
cdataplot=ggplot(Trtdata, aes(x=BSpecies,y=mean))+geom_bar(aes(fill = Phylum),colour="black", stat="identity")+xlab("Bird Species")+ylab("Relative Abundance (> 0.01%)")+theme(axis.title.x=element_blank())+ theme(axis.text.x = element_text(angle = 45, hjust = 1))+ scale_fill_manual(values=cbPalette)
cdataplot#+  scale_x_discrete(labels=c("0 hrs", "24 hrs", "48 hrs","72 hrs"))
#position = "fill"#+geom_errorbar(aes(ymin=mean-se,ymax=mean+se),color="black",width=1)+geom_line(size=1.5,linetype="dashed")+geom_point(size=6)+ylab(
cdataplot=ggplot(PhylumAll3, aes(x=Month,y=mean))+geom_bar(aes(fill = Phylum),colour="black", stat="identity")+xlab("Month")+ylab("Relative Abundance (> 0.01%)")+theme(axis.title.x=element_blank())+ theme(axis.text.x = element_text(angle = 45, hjust = 1))+facet_wrap(~BSpecies)+ scale_fill_manual(values=cbPalette)
cdataplot
```

```{r,warning=FALSE}
#SigLetters<-c("a","ab","a","bc","c","a","a","b","b","b","ab","c","ac","bd","d","abc","a","ab", "bc","c","ab","a","b","b","c","ab","ab","a","ab","b","ab","a","bc","c","c","ab","a","ab","bc","c")#Taken from output 
NComparisons<-length(unique(metadata$BSpecies))*length(unique(Trtdata$Phylum))
SigList<-length(unique(Trtdata$Phylum))
SigLetters2<-vector(length=NComparisons)
#vec<-unlist(lst)
Means=compare_means(Abundance ~ BSpecies, data = df, group.by = "Phylum", p.adjust.method = "fdr")
for (i in levels(Means$Phylum)){
  Tax<-i
  TaxAbundance<-subset(Means,Phylum==i )
  Hyphenated<-as.character(paste0(TaxAbundance$group1,"-",TaxAbundance$group2))
  difference<-TaxAbundance$p.adj
  names(difference)<-Hyphenated
  Letters<-multcompLetters(difference)
  #print(Letters)
  SigList[i]<-Letters
  
}
vec<-unlist(SigList)
vec<-vec[-1]

cdataplot=ggplot(Trtdata, aes(x=BSpecies,y=mean))+geom_bar(aes(fill = BSpecies),colour="black", stat="identity")+ facet_grid(~Phylum)+xlab("Bird Species")+ylab("Relative Abundance (> 0.01%)") + theme(axis.text.x = element_text(angle = 45, hjust = 1))+theme(axis.title.x=element_blank())+facet_wrap(~Phylum)+geom_errorbar(aes(ymin=mean-se,ymax=mean+se))+geom_text(aes(x=BSpecies, y=mean+se+10,label=vec))+ scale_fill_manual(values=cbPalette)
#scale_x_discrete(labels=c("0 hrs", "24 hrs", "48 hrs","72 hrs"))+ theme(axis.text.x = element_text(angle = 45, hjust = 1))#+ scale_fill_manual(values=cbPalette)
cdataplot
```


###Family Level

The top 5 Families across all samples are given in the table below
```{r Summarizing2,warning=FALSE}
df <- psmelt(FamilyLevel)
df$Abundance=df$Abundance*100
Trtdata <- ddply(df, c("Family", "BSpecies"), summarise,
                 N    = length(Abundance),
                 mean = mean(Abundance),
                 sd   = sd(Abundance),
                 se   = sd / sqrt(N)
)

df2 <- psmelt(FamilyAll)
df2$Abundance<-df2$Abundance*100
FamilyAll<-ddply(df2, c("Family"), summarise,
                 N    = length(Abundance),
                 mean = mean(Abundance),
                 sd   = sd(Abundance),
                 se   = sd / sqrt(N)
)
FamilySorted<-FamilyAll[order(-FamilyAll$mean),]
FamilySorted[1:5,]
Trtdata
FamilyAll2<-ddply(df2, c("Family","BSpecies"), summarise, #For Rel abu tabs
                  N    = length(Abundance),
                  mean = mean(Abundance),
                  sd   = sd(Abundance),
                  se   = sd / sqrt(N)
)
FamilySorted2<-FamilyAll2[order(-FamilyAll$mean),]

FamilyAll3<-ddply(df, c("Family","Month","BSpecies"), summarise, #For Rel abu tabs
                  N    = length(Abundance),
                  mean = mean(Abundance),
                  sd   = sd(Abundance),
                  se   = sd / sqrt(N)
)
```




```{r TreatmentPlot,warning=FALSE}
cdataplot=ggplot(Trtdata, aes(x=BSpecies,y=mean))+geom_bar(aes(fill = Family),colour="black", stat="identity")+xlab("BSpecies")+ylab("Relative Abundance (> 0.1%)")+theme(axis.title.x=element_blank())+ theme(axis.text.x = element_text(angle = 45, hjust = 1))+ scale_fill_manual(values=cbPalette)
cdataplot#+  scale_x_discrete(labels=c("0 hrs", "24 hrs", "48 hrs","72 hrs"))
cdataplot=ggplot(FamilyAll3, aes(x=Month,y=mean))+geom_bar(aes(fill = Family),colour="black", stat="identity")+xlab("Month")+ylab("Relative Abundance (> 0.1%)")+theme(axis.title.x=element_blank())+ theme(axis.text.x = element_text(angle = 45, hjust = 1))+facet_wrap(~BSpecies)+ scale_fill_manual(values=cbPalette)
cdataplot
#position = "fill"#+geom_errorbar(aes(ymin=mean-se,ymax=mean+se),color="black",width=1)+geom_line(size=1.5,linetype="dashed")+geom_point(size=6)+ylab(

NComparisons<-length(unique(metadata$BSpecies))*length(unique(Trtdata$Family))
SigList<-length(unique(Trtdata$Family))
SigLetters2<-vector(length=NComparisons)
#vec<-unlist(lst)
Means=compare_means(Abundance ~ BSpecies, data = df, group.by = "Family", p.adjust.method = "fdr")
for (i in levels(Means$Family)){
  Tax<-i
  TaxAbundance<-subset(Means,Family==i )
  Hyphenated<-as.character(paste0(TaxAbundance$group1,"-",TaxAbundance$group2))
  difference<-TaxAbundance$p.adj
  names(difference)<-Hyphenated
  Letters<-multcompLetters(difference)
  #print(Letters)
  SigList[i]<-Letters
  
}
vec<-unlist(SigList)
vec<-vec[-1]

cdataplot=ggplot(Trtdata, aes(x=BSpecies,y=mean))+geom_bar(aes(fill = BSpecies),colour="black", stat="identity")+ facet_grid(~Family)+xlab("Bird Species")+ylab("Relative Abundance (0.1%)") + theme(axis.text.x = element_text(angle = 45, hjust = 1))+theme(axis.title.x=element_blank())+facet_wrap(~Family)+geom_errorbar(aes(ymin=mean-se,ymax=mean+se))+geom_text(aes(x=BSpecies, y=mean+se+5,label=vec))+scale_fill_manual(values=cbPalette)
cdataplot


```



###Genus level
The top 5 genera across all samples are given in the table below
```{r Summarizing3,warning=FALSE}
df <- psmelt(GenusLevel)
df$Abundance=df$Abundance*100
Trtdata <- ddply(df, c("Genus", "BSpecies"), summarise,
                 N    = length(Abundance),
                 mean = mean(Abundance),
                 sd   = sd(Abundance),
                 se   = sd / sqrt(N)
)
df2 <- psmelt(GenusAll)
df2$Abundance<-df2$Abundance*100
GenusAll<-ddply(df2, c("Genus"), summarise,
                N    = length(Abundance),
                mean = mean(Abundance),
                sd   = sd(Abundance),
                se   = sd / sqrt(N)
)
GenusSorted<-GenusAll[order(-GenusAll$mean),]
GenusSorted[1:5,]
Trtdata
GenusAll2<-ddply(df2, c("Genus","BSpecies"), summarise, #For Rel abu tabs
                 N    = length(Abundance),
                 mean = mean(Abundance),
                 sd   = sd(Abundance),
                 se   = sd / sqrt(N)
)
GenusSorted2<-GenusAll2[order(-GenusAll$mean),]

GenusAll3<-ddply(df, c("Genus","BSpecies","Month"), summarise, #For Rel abu tabs
                 N    = length(Abundance),
                 mean = mean(Abundance),
                 sd   = sd(Abundance),
                 se   = sd / sqrt(N)
)
GenusAll3
```

```{r TreatmentPlot4,warning=FALSE}
NComparisons<-length(unique(metadata$BSpecies))*length(unique(Trtdata$Genus))
SigList<-length(unique(Trtdata$Genus))
SigLetters2<-vector(length=NComparisons)

Means=compare_means(Abundance ~ BSpecies, data = df, group.by = "Genus", p.adjust.method = "fdr")
#vec<-unlist(lst)
for (i in levels(Means$Genus)){
  Tax<-i
  TaxAbundance<-subset(Means,Genus==i )
  #print(TaxAbundance)
  Hyphenated<-as.character(paste0(TaxAbundance$group1,"-",TaxAbundance$group2))
  difference<-TaxAbundance$p.adj
  names(difference)<-Hyphenated
  Letters<-multcompLetters(difference)
  #print(Letters)
  SigList[i]<-Letters
  
}
vec<-unlist(SigList)
vec<-vec[-1]
cdataplot=ggplot(Trtdata, aes(x=BSpecies,y=mean))+geom_bar(aes(fill = Genus),colour="black", stat="identity")+xlab("Bird BSpecies")+ylab("Relative Abundance (> 0.1%)") + theme(axis.text.x = element_text(angle = 0, hjust = 0.5))+theme(axis.title.x=element_blank())+ theme(axis.text.x = element_text(angle = 45, hjust = 1))+ scale_fill_manual(values=cbPalette)#+geom_text(aes(x=BSpecies, y=mean+se+10,label=vec))
cdataplot#+  scale_x_discrete(labels=c("0 hrs", "24 hrs", "48 hrs","72 hrs"))

cdataplot=ggplot(GenusAll3, aes(x=Month,y=mean))+geom_bar(aes(fill = Genus),colour="black", stat="identity")+xlab("Month")+ylab("Relative Abundance (> 0.1%)") + theme(axis.text.x = element_text(angle = 0, hjust = 0.5))+theme(axis.title.x=element_blank())+ theme(axis.text.x = element_text(angle = 45, hjust = 1))+facet_wrap(~BSpecies)+ scale_fill_manual(values=cbPalette)#+geom_text(aes(x=BSpecies, y=mean+se+10,label=vec))
cdataplot#+  scale_x_discrete(labels=c("0 hrs", "24 hrs", "48 hrs","72 

#position = "fill"#+geom_errorbar(aes(ymin=mean-se,ymax=mean+se),color="black",width=1)+geom_line(size=1.5,linetype="dashed")+geom_point(size=6)+ylab(

#+ theme(axis.text.x = element_text(angle = 45, hjust = 1))#+ scale_fill_manual(values=cbPalette)
compare_means(Abundance~BSpecies, data=df,group.by="Genus",method = "kruskal.test",p.adjust.method="fdr")

Means=compare_means(Abundance ~ BSpecies, data = df, 
                    group.by = "Genus", p.adjust.method = "fdr")
# #head(Means)
# keeps <- c("Genus","group1","group2","p.adj","method","p.signif")
# keeps=Means[keeps]
# #keeps
# 
# 
# test3 <- list('Genus'= keeps$Genus,'group1'=keeps$group1,'group2'= keeps$group2,'p.adj'=keeps$p.adj)
# test3= as.data.frame(test3)
# #test3
# FilteredResults<-test3[!(test3$p.adj>0.05),]            
# FilteredResults

```



###PhylumAbuAll

Below is a list of the relative abundance of all taxa at the Phylum level by BSpecies
```{r}
df <- psmelt(PhylumLevel)
df$Abundance=df$Abundance*100
Trtdata <- ddply(df, c("Phylum", "BSpecies"), summarise,
                 N    = length(Abundance),
                 mean = mean(Abundance),
                 sd   = sd(Abundance),
                 se   = sd / sqrt(N)
)

```

```{r}
compare_means(Abundance~BSpecies, data=df,group.by="Phylum",method = "kruskal.test",p.adjust.method="fdr")
Means=compare_means(Abundance ~ BSpecies, data = df, 
                    group.by = "Phylum", p.adjust.method = "fdr")

```

Multiple comparisons for all taxa grouped by Phylum
```{r}

NComparisons<-length(unique(metadata$BSpecies))*length(unique(Trtdata$Phylum))
SigList<-length(unique(Trtdata$Phylum))
SigLetters2<-vector(length=NComparisons)
#vec<-unlist(lst)
for (i in levels(Means$Phylum)){
  Tax<-i
  TaxAbundance<-subset(Means,Phylum==i )
  print(TaxAbundance)
  Hyphenated<-as.character(paste0(TaxAbundance$group1,"-",TaxAbundance$group2))
  difference<-TaxAbundance$p.adj
  names(difference)<-Hyphenated
  Letters<-multcompLetters(difference)
  print(Letters)
  
}


```

###FamilyAbuAll
Below is a list of the relative abundance of all taxa at the Family level by BSpecies
```{r}
df <- psmelt(FamilyLevel)
df$Abundance=df$Abundance*100
Trtdata <- ddply(df, c("Family", "BSpecies"), summarise,
                 N    = length(Abundance),
                 mean = mean(Abundance),
                 sd   = sd(Abundance),
                 se   = sd / sqrt(N)
)

```

```{r}
compare_means(Abundance~BSpecies, data=df,group.by="Family",method = "kruskal.test",p.adjust.method="fdr")
Means=compare_means(Abundance ~ BSpecies, data = df, 
                    group.by = "Family", p.adjust.method = "fdr")

```

Multiple comparisons for all taxa grouped by Family
```{r}

NComparisons<-length(unique(metadata$BSpecies))*length(unique(Trtdata$Family))
SigList<-length(unique(Trtdata$Family))
SigLetters2<-vector(length=NComparisons)
#vec<-unlist(lst)
for (i in levels(Means$Family)){
  Tax<-i
  TaxAbundance<-subset(Means,Family==i )
  print(TaxAbundance)
  Hyphenated<-as.character(paste0(TaxAbundance$group1,"-",TaxAbundance$group2))
  difference<-TaxAbundance$p.adj
  names(difference)<-Hyphenated
  Letters<-multcompLetters(difference)
  print(Letters)
  
}



```

###GenusAbuAll

Below is a list of the relative abundance of all taxa at the Genus level by BSpecies
```{r}
GenusSorted2
```




##PCoA {.tabset}

###Weighted Unifrac
-Ellipses represent 95% CI for the mean of each group
```{r PCoA, warning=FALSE}
ord=ordinate(physeq,"PCoA", "wunifrac")
ordplot=plot_ordination(physeq, ord,"samples", color="BSpecies")+geom_point(size=4)+scale_colour_manual(values=cbPalette)+scale_fill_manual(values=cbPalette)
ordplot+ stat_ellipse(type= "norm",geom = "polygon", alpha = 1/4, aes(fill = BSpecies))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())#+ theme(legend.justification=c(1,0), legend.position=c(1,0))

```

```{r PCoA2, warning=FALSE}
ord=ordinate(physeq,"PCoA", "wunifrac")
ordplot=plot_ordination(physeq, ord,"samples", color="Month")+geom_point(size=4)+scale_colour_manual(values=cbPalette)+scale_fill_manual(values=cbPalette)
ordplot+ stat_ellipse(type= "norm",geom = "polygon", alpha = 1/4, aes(fill = Month))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())#+ theme(legend.justification=c(1,0), legend.position=c(1,0))

```

###Jaccard
-Ellipses represent 95% CI for the mean of each group
```{r PCoA3, warning=FALSE}
ord=ordinate(physeq,"PCoA", "jaccard")
ordplot=plot_ordination(physeq, ord,"samples", color="BSpecies")+geom_point(size=4)+scale_colour_manual(values=cbPalette)+scale_fill_manual(values=cbPalette)
ordplot+ stat_ellipse(type= "norm",geom = "polygon", alpha = 1/4, aes(fill = BSpecies))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())#+ theme(legend.justification=c(1,0), legend.position=c(1,0))

```

```{r PCoA4, warning=FALSE}
ord=ordinate(physeq,"PCoA", "jaccard")
ordplot=plot_ordination(physeq, ord,"samples", color="Month")+geom_point(size=4)+scale_colour_manual(values=cbPalette)+scale_fill_manual(values=cbPalette)
ordplot+ stat_ellipse(type= "norm",geom = "polygon", alpha = 1/4, aes(fill = Month))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())#+ theme(legend.justification=c(1,0), legend.position=c(1,0))

```

###Bray-curtis
-Ellipses represent 95% CI for the mean of each group
```{r PCoA5, warning=FALSE}
ord=ordinate(physeq,"PCoA", "bray")
ordplot=plot_ordination(physeq, ord,"samples", color="BSpecies")+geom_point(size=4)+scale_colour_manual(values=cbPalette)+scale_fill_manual(values=cbPalette)
ordplot+ stat_ellipse(type= "norm",geom = "polygon", alpha = 1/4, aes(fill = BSpecies))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())#+ theme(legend.justification=c(1,0), legend.position=c(1,0))

```

```{r PCoA6, warning=FALSE}
ord=ordinate(physeq,"PCoA", "bray")
ordplot=plot_ordination(physeq, ord,"samples", color="Month")+geom_point(size=4)+scale_colour_manual(values=cbPalette)+scale_fill_manual(values=cbPalette)
ordplot+ stat_ellipse(type= "norm",geom = "polygon", alpha = 1/4, aes(fill = Month))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())#+ theme(legend.justification=c(1,0), legend.position=c(1,0))

```

##PERMANOVAs {.tabset}
###Weighted Unifrac
####Homogenieity of Multivariate Dispersions
```{r, warning=FALSE}
GPdist=phyloseq::distance(physeq, "wunifrac")
beta=betadisper(GPdist, sample_data(physeq)$BSpecies)
permutest(beta)
boxplot(beta)
```


``` {r wunifracPERMANOVAs,warning=FALSE}
GPdist=phyloseq::distance(physeq, "wunifrac")
#MONMDS= ordinate(physeq, "NMDS",GPdist)
```

```{r}
adonis(GPdist ~ BSpecies*Month, as(sample_data(physeq), "data.frame"))
```


###Jaccard
####Homogenieity of Multivariate Dispersions
```{r, warning=FALSE}
GPdist=phyloseq::distance(physeq, "jaccard")
beta=betadisper(GPdist, sample_data(physeq)$BSpecies)
permutest(beta)
boxplot(beta)
```

####Species
``` {r jaccardPERMANOVAs,warning=FALSE}
GPdist=phyloseq::distance(physeq, "jaccard")
#MONMDS= ordinate(physeq, "NMDS",GPdist)
```

```{r}
adonis(GPdist ~ BSpecies*Month, as(sample_data(physeq), "data.frame"))
```

####RTHA subset
``` {r jaccardPERMANOVAs2,warning=FALSE}
RTHAPhyseq<-subset_samples(physeq,BSpecies=="RTHA")
GPdist=phyloseq::distance(RTHAPhyseq, "jaccard")
#MONMDS= ordinate(physeq, "NMDS",GPdist)
```

```{r}
adonis(GPdist ~ Month, as(sample_data(RTHAPhyseq), "data.frame"))
adonis(GPdist ~ Year, as(sample_data(RTHAPhyseq), "data.frame"))

```


###Bray-curtis
####Homogenieity of Multivariate Dispersions
```{r, warning=FALSE}
GPdist=phyloseq::distance(physeq, "bray")
beta=betadisper(GPdist, sample_data(physeq)$BSpecies)
permutest(beta)
boxplot(beta)
```


``` {r brayPERMANOVAs,warning=FALSE}
GPdist=phyloseq::distance(physeq, "bray")
#MONMDS= ordinate(physeq, "NMDS",GPdist)
```

```{r}
adonis(GPdist ~ BSpecies*Month, as(sample_data(physeq), "data.frame"))
```

##Random Forest {.tabset}
###By BSpecies
```{r Forest1}
options(max.print=1000000)
ForestData=GenusLevel#Change this one so you dont have to rewrite all variables
predictors=t(otu_table(ForestData))
response <- as.factor(sample_data(ForestData)$BSpecies)
rf.data <- data.frame(response, predictors)
MozzieForest <- randomForest(response~., data = rf.data, ntree = 1000)
print(MozzieForest)#returns overall Random Forest results
imp <- importance(MozzieForest)#all the steps that are imp or imp. are building a dataframe that contains info about the taxa used by the Random Forest testto classify treatment 
imp <- data.frame(predictors = rownames(imp), imp)
imp.sort <- arrange(imp, desc(MeanDecreaseGini))
imp.sort$predictors <- factor(imp.sort$predictors, levels = imp.sort$predictors)
imp.20 <- imp.sort[1:20, ]
ggplot(imp.20, aes(x = predictors, y = MeanDecreaseGini)) +
  geom_bar(stat = "identity", fill = "indianred") +
  coord_flip() +
  ggtitle("Most important genera for classifying  samples\n by Bird Species")#\n in a string tells it to start a new line
#imp.20$MeanDecreaseGini
otunames <- imp.20$predictors
r <- rownames(tax_table(ForestData)) %in% otunames
kable(tax_table(ForestData)[r, ])#returns a list of the most important predictors for Random Forest Classification
```

